Minicaml, a purely functional, didactical programming language with an interactive REPL. WORK IN PROGRESS DRAFT

### 2019-12-25 paper/paper.tex
opam version bump and paper progress

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework. Code
coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
page when tests are run by dune.

>>>>

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework. Code
coverage is provided by the \texttt{bisect\_ppx} library which yields an HTML
page containing the coverage percentage when unit tests are run by the dune
build system. After each commit is pushed to the remote source repository on
Github, the package is built and tests are run by the Travis Continuos
Integration system.
